
\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Rudraksha Singh Sengar}} & Email: \href{mailto:}{rudraksharss@gmail.com}\\
  \href{https://github.com/rudrakshass}{Github: github.com/rudrakshass} & Mobile:+91-708-1499-993 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dayananda Sagar College of Engineering, Bangalore}{Karnataka, India}
      {Bachelor of Engineering - Computer Science and Engineering; \textbf{SGPA:8.2}}{November 2023}
       
    \resumeSubHeadingListEnd    
\vspace{5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{Python, C, C++, \textbf{JavaScript, TypeScript}}
	\resumeSubItem{Frontend Frameworks}{\textbf{React}, \textbf{Next.js}}
    \resumeSubItem{CSS Frameworks}{\textbf{Tailwind CSS}}
	\resumeSubItem{Tools}{\textbf{Git/Github}}
	\resumeSubItem{Platforms}{Windows, Linux}
	\resumeSubHeadingListEnd

\vspace{5pt}
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
  {RemoteStar}{Remote}
  {Frontend Developer: Next.js, Typescript, Framer Motion, Tailwind CSS}{March 2025 - Present}

  \resumeItemListStart

    \resumeItem{Frontend Development}
      {Developed the entire frontend of RemoteStar’s website using \textbf{Next.js}, \textbf{Tailwind CSS}, and \textbf{Framer Motion}.}

    \resumeItem{UI/UX Design}
      {Designed an intuitive and visually appealing user interface for an \textbf{AI-powered online interview platform}.}

    \resumeItem{Backend Connectivity}
      {Integrated the frontend with the backend, ensuring seamless \textbf{API communication} and \textbf{data flow}.}

  \resumeItemListEnd

\resumeSubHeadingListEnd

    
\vspace{5pt}
\section{Open Source Contributions}
\resumeSubHeadingListStart
	\resumeSubItem{Hacktoberfest 2024}{Successfully completed 4 pull requests (PRs) contributing to open-source projects during Hacktoberfest. 
		\begin{itemize}
			\item Added an \textbf{export button} to a website, allowing users to export datasets in CSV, JSON, and TXT formats.
			\item Implemented \textbf{hover-over tooltips} that describe the functionality of the export button.
			\item Customized the \textbf{front-end design} of buttons to improve the user interface and overall user experience.
			\item Designed and added a \textbf{favicon} to the website for improved branding and visual appeal.
		\end{itemize}
	}
\resumeSubHeadingListEnd

\vspace{5pt}
\section{Volunteering}
  \resumeSubHeadingListStart

\resumeSubheading
  {PointBlank (Coding Club)}{Member}
  {Frontend Developer: Next.js, Typescript, Framer Motion, Tailwind CSS, Cloudinary}{February 2025 - Present}

\resumeItemListStart
  \resumeItem{Custom Loader}
    {Designed and implemented a reusable, aesthetic \textbf{Framer Motion}-based loader displayed across all pages.}
    
  \resumeItem{Lore Page}
    {Built the entire \href{https://pointblank.club/lore}{\textcolor{blue}{/lore}} page — from \textbf{UI/UX design} to responsive frontend development using \textbf{Next.js} and \textbf{Tailwind CSS}.}
    
  \resumeItem{PBCTF Form Page}
    {Designed and developed the full \href{https://pointblank.club/pbctf}{\textcolor{blue}{/pbctf}} registration page, including form logic, UI, and frontend implementation.}
\resumeItemListEnd
\vspace{5pt}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\vspace{2pt}
\resumeSubItem{Zenith – 36-hour Competitive Tech Event  
\href{https://github.com/pbdsce/zenith}{\color{blue}{GitHub}}/\href{https://zenith.pointblank.club}{\color{blue}{Deployment}}} {
    \begin{itemize}
        \item Designed the entire \textbf{UI/UX} and developed the \textbf{front-end} for the event website.  
        \item Built a responsive, high-performance website using \textbf{Next.js} and \textbf{Tailwind CSS}.  
        \item Ensured seamless \textbf{user experience} with intuitive navigation, accessibility, and optimized performance.  
        \item Tech: \textbf{Next.js}, \textbf{TypeScript}, \textbf{Tailwind CSS}, \textbf{Framer Motion} 
    \end{itemize}
    }

\resumeSubItem{Sinkedin - A platform to celebrate failure  \href{https://github.com/rudrakshass/Sinkedin}{\color{blue}{GitHub}}/\href{https://sinkedin.xyz}{\color{blue}{Deployment}}} {
    \begin{itemize}
        \item Developed a platform allowing users to share their failures and gain community support.
        \item Built the \textbf{front-end} using \textbf{React}, \textbf{TypeScript}, and \textbf{Tailwind CSS}.
        \item Styled with \textbf{Tailwind}, ensuring a clean, modern design for desktop and mobile.
        \item Tech: \textbf{Next.js}, \textbf{TypeScript}, \textbf{Tailwind CSS}, \textbf{Framer Motion}
    \end{itemize}
}

\resumeSubHeadingListEnd

\vspace{5pt}
\section{Achievements}
\resumeSubHeadingListStart
  \resumeSubItem{Technical Escape Room (CTF)}{Secured \textbf{1st place} among 35 teams in a competitive, time-bound Capture The Flag challenge — March 2025.}
  \resumeSubItem{NER Tech Hackathon}{Selected as a \textbf{Finalist} in a national-level hackathon organized by \textbf{Amantya Technologies}.}
  \resumeSubItem{Aventus Hackathon}{Selected as a \textbf{Finalist} in a hackathon organized by \textbf{Dayananda Sagar College of Engineering}.}
\resumeSubHeadingListEnd
\end{document}
